% -- Encoding UTF-8 without BOM
% -- XeLaTeX => PDF (BIBER)

\documentclass[]{cv-style}          % Add 'print' as an option into the square bracket to remove colours from this template for printing. 
                                    % Add 'espanol' as an option into the square bracket to change the date format of the Last Updated Text

\sethyphenation[variant=british]{english}{} % Add words between the {} to avoid them to be cut 
\usepackage{marvosym}
\usepackage{fontawesome5}

\begin{document}

\header{Patryk }{Choma}           % Your name
\lastupdated

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION  -- In the aside, each new line forces a line break
%----------------------------------------------------------------------------------------

\begin{aside}
%
\section{contact}
Via Pasquale II 53
00168, Rome
Italy
~
{\Telefon} 346 392 4445 \\(\textbf{book call via eMail})
~
{\Email} patryk.choma
@gmail.com
%
\section{web}
\faIcon{globe} \href{https://ch-pat.github.io/}{\underline{website}}
~
\faIcon{linkedin} \href{https://www.linkedin.com/in/p-choma/}{\underline{LinkedIn}}
~
\faIcon{github} \href{https://github.com/ch-pat}{\underline{GitHub}}
%
\section{languages}
\textbf{Italian} mother tongue
\textbf{English} high
%
\section{programming}
\textbf{Python}
Node.js
Java
Go
%
\section{technologies}
\textbf{Google Cloud Platform}
Spanner, BigQuery, BigTable
Cloud Functions
Git, Bash, SQL
Jest, Express
Angular, HTML, CSS
Flask, Selenium, Behave
Android, Linux, Windows
%
\section{soft skills}
Listening 
Succinct Writing
Adaptability
Patience
Desire to learn
Logical thinking
Problem Solving
\end{aside}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

\begin{entrylist}
%------------------------------------------------
\entry
{2022--Now}
{NTT Data}
{Rome, Italy}
{\jobtitle{Software Developer Engineer}\\
Work on Assicurazioni Generali's NextJenIoT project dealing with black boxes installed on cars for insurance purposes.\\
The project lives within the Google Cloud Platform ecosystem: The APIs are deployed as Google Cloud Functions and the data is stored on Spanner and BigQuery tables.\\
I built, designed, deployed and maintained APIs (in Python and Nodejs) to read and interact with all device data, such as gps and acceleration data of trips and crashes.\\
I developed both unit and integration tests to cover all use cases and extensively documented my work.}
%------------------------------------------------
\entry
{2021--2022}
{Ericsson}
{Rome, Italy}
{\jobtitle{VMWare Operation Engineer}\\
Managed network configurations and troubleshooted issues within the VMWare cloud stack.}
%------------------------------------------------
\entry 
  {2020--2021}
  {Freelancing}
  {Rome, Italy}
  {\jobtitle{Freelance Developer}\\
  Commissioned work on two python desktop apps with simple UIs:
  \begin{itemize}
      \item Interface for Synology NAS to handle file upload, user creation, notification and receipt confirmation.
      \item User friendly CRUD interface for modifying Excel files using Pandas.
  \end{itemize}
}
%------------------------------------------------
\entry
  {2018--2021}
  {Amministrazioni Martellucci}
  {Rome, Italy}
  {\jobtitle{Accounting and IT support}\\
  Managed, tracked and documented the accounting. Improved workflow with excel worksheets and python scripts.
  }
%------------------------------------------------
\entry
  {2010--2020}
  {Tuition}
  {Rome, Italy}
  {\jobtitle{Private tutor}\\
    Math and English language tuition lessons. Funded my studies, taught me patience and how to teach others.
  }
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{entrylist}
%------------------------------------------------
\entry
{2020--Now}
{Master's Degree in Computer Science}
{Sapienza Università di Roma | Rome, Italy}
{Continuing my CS studies. Courses are mostly focused on: 
\begin{itemize}
    \item Data Science, Machine Learning and AI
    \item Computer Vision and Computer Graphics
    \item Cloud Computing and Big Data
\end{itemize}
}
\entry
{2016--2020}
{Bachelor's Degree in Computer Science}
{Sapienza Università di Roma | Rome, Italy}
{I learned all CS fundamentals, such as:
\begin{itemize}
    \item Algorithms and Data Structures
    \item Relational Database Design
    \item Object Oriented Programming
\end{itemize}
My thesis was based on my work on a new API for the SeismoCloud project, which queries a MySQL database, was written in Go and deployed using Docker.
}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	SOFT SKILLS SECTION
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%		INTERESTS SECTION
%----------------------------------------------------------------------------------------
\section{Interests}

\begin{entrylist}
%------------------------------------------------
\entry
{} %{Professional}
{{\normalfont 
Expand my skillset, work on useful and interesting projects on different tech stacks. My main interests lie in back-end, testing and automation development but I don't mind branching out every once in a while.}}
{}
{\vspace{-0.5cm}}
%------------------------------------------------
\end{entrylist}
\end{document}